\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-02-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added link to online supplement

{\color{blue} For each replication we compute the ratio of the loss of each alternative reconciliation method to the loss of base forecasts. A value less than 1 indicates that a reconciliation method has a lower relative error than the base forecast for that replication, while a value greater than 1 indicates the opposite. The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of these ratios over each rolling window. We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons. We do not present these here to save space but they are available {\color{red} in an online supplement.}

@@

Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons. We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts.%, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$. 
Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}. The Friedman test first establishes whether at least one of the forecasts is significantly different from the rest. If this is the case, we use the Nemenyi test to identify groups of forecasts for which there is no evidence of statistically significant differences. This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests. We use the implementation of the tests available in the \verb"tsutils " \citep{tsutils} package for R.}

>>>>

{\color{blue} For each replication we compute the ratio of the loss of each alternative reconciliation method to the loss of base forecasts. A value less than 1 indicates that a reconciliation method has a lower relative error than the base forecast for that replication, while a value greater than 1 indicates the opposite. The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of these ratios over each rolling window. We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons. We do not present these here to save space but they are available in an online supplement\footnote{Available at \url{https://anastasiospanagiotelis.netlify.com/papers/GeomRecoSupplement.pdf}}.

@@

Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons. We do not present these here to save space but they are available at \url{https://anastasiospanagiotelis.netlify.com/papers/GeomRecoSupplement.pdf}.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts.%, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$. 
Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}. The Friedman test first establishes whether at least one of the forecasts is significantly different from the rest. If this is the case, we use the Nemenyi test to identify groups of forecasts for which there is no evidence of statistically significant differences. This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests. We use the implementation of the tests available in the \verb"tsutils " \citep{tsutils} package for R.}
